\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-21 draft.tex
distinguish all Z/ZN in appendix; at least note where changes to proofs result

Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$ as long as $\tau^a$ is weakly larger than the optimal unilateral tariff in the absence of lobbying, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$. Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.  $\hfill\blacksquare$

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_tad_dir}{Proof of Lemma~\ref{res:tad_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tad$; to show that the renewal probability is decreasing in $\tad$, I must demonstrate that this derivative is positive. Again labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tad$ is

\begin{equation}
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right) + Z(\bta,\tad) \frac{\partial \pi_X(\tad)}{\partial \tad}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:tad}
\end{equation}

@@

$Z(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum. Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$. With a positive denominator, we thus have that the entire express is positive on $[0,\tau^O]$.

@@

Then $\frac{\partial^2 r}{\partial e \partial \tad} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tad} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tad \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. As long as $\tad$ is greater than the optimal unilateral tariff, $\frac{\partial Z(\bta,\tad)}{\partial \tad} \leq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tad} \geq 0$. Thus $\frac{\partial e}{\partial \tad} \leq 0$.  $\hfill\blacksquare$

@@

\vskip.4in

\newpage
\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.

@@

\vskip.4in
\newpage
\noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that the following derivative is negative: 
\[
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\]

@@

Then $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \pi(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $-\frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$. Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.  $\hfill\blacksquare$

>>>>

Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$. Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.  $\hfill\blacksquare$

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_tad_dir}{Proof of Lemma~\ref{res:tad_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tad$; to show that the renewal probability is decreasing in $\tad$, I must demonstrate that this derivative is positive. Again labeling the numerator of that expression $ZN(\bta,\tad)$, the derivative of this quantity with respect to $\tad$ is

\begin{equation}
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right) + ZN(\bta,\tad) \frac{\partial \pi_X(\tad)}{\partial \tad}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:tad}
\end{equation}

@@

$ZN(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum. Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$. With a positive denominator, we thus have that the entire express is positive on $[0,\tau^O]$.

@@

Then $\frac{\partial^2 r}{\partial e \partial \tad} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tad} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tad \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $\frac{\partial Z(\bta,\tad)}{\partial \tad} \geq 0$ by the proof of Lemma~\ref{res:tad_dir}, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tad} \leq 0$. Thus the sign of $\frac{\partial e}{\partial \tad}$ is ambiguous.  $\hfill\blacksquare$

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.

@@

\vskip.4in
\noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that the following derivative is negative: 
\[
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + ZN(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\]

@@

Then $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \pi(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. Refer to result in proof of Lemma~\ref{res:pi_dir}; then $\frac{\partial f_\ga}{\partial e} \geq 0$ implies that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \ldots$. Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.  $\hfill\blacksquare$
